Clustering and Parameter Estimation for the Popularity Adjusted Block Model

### 2020-07-13 summary.Rmd
minor updates to writeup

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \KwData{Edge probability matrix $P$, number of clusters $K$}
  \KwResult{Cluster assignments $1, ..., K$}
    Compute the spectral decomposition $P = V D V^\top$\;
    Compute the inner product matrix $B = V V^\top$\;
    Identify the connected components and map each to clusters $1..K$\;
  \caption{PABM clustering on the edge probability matrix}
\end{algorithm}

@@

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \KwData{Adjacency matrix $A$, number of clusters $K$}
  \KwResult{Cluster assignments $1, ..., K$}
    Compute the eigenvectors of $A$ that correspond to the $K (K+1) / 2$ most 
    positive eigenvalues and $K (K-1) / 2$ most negative eigenvalues. Construct 
    $V$ using these eigenvectors as its columns.\;
    Compute $B = V V^\top$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected components 
    (e.g., using edge thresholding or spectral clustering).\;
    Map each connected components as the clusters $1, ..., K$.\;
  \caption{PABM clustering on the adjacency matrix}
\end{algorithm}

@@

```{r q_trans, fig.cap = 'Pair plots of $ZQ$ where $Q$ was found by minimizing objective function (1). This embedding is equivalent to $XU$ up to a 90-degree rotation.'}
XU.prime <- transform.embedding(Z, z)
pairs(XU.prime, col = z, asp = 1)
```

@@

```{r}
XU.hat <- transform.embedding(Zhat, z)
pairs(XU.hat, col = z, asp = 1)
```

>>>>

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \KwData{Edge probability matrix $P$, number of clusters $K$}
  \KwResult{Cluster assignments $1, ..., K$}
    Compute the spectral decomposition $P = V D V^\top$.\;
    Compute the inner product matrix $B = V V^\top$.\;
    Construct graph $G$ using $B$ as edge similarities.\;
    Identify the connected components and map each to cluster labels $1, ..., K.$\;
  \caption{PABM clustering on the edge probability matrix}
\end{algorithm}

@@

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \KwData{Adjacency matrix $A$, number of clusters $K$}
  \KwResult{Cluster assignments $1, ..., K$}
    Compute the eigenvectors of $A$ that correspond to the $K (K+1) / 2$ most 
    positive eigenvalues and $K (K-1) / 2$ most negative eigenvalues. Construct 
    $V$ using these eigenvectors as its columns.\;
    Compute $B = V V^\top$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected components 
    (e.g., using edge thresholding or spectral clustering).\;
    Map each of the connected components to the cluster labels $1, ..., K$.\;
  \caption{PABM clustering on the adjacency matrix}
\end{algorithm}

@@

```{r q_trans, fig.cap = 'Pair plots of $ZQ$ where $Q$ was found by minimizing objective function (1). This embedding is equivalent to $XU$ up to 90-degree rotations and reflection along axes.'}
XU.prime <- transform.embedding(Z, z)
pairs(XU.prime, col = z, asp = 1)
```

@@

```{r q_from_a, fig.cap = 'Pair plots of $\\hat{Z} $ where $\\hat{Z}$ is the ASE of an adjacency matrix of a PABM and $Q$ is estimated by minimizing objective function (1).'}
XU.hat <- transform.embedding(Zhat, z)
pairs(XU.hat, col = z, asp = 1)

# X.hat <- XU.hat %*% t(U)
# plot(abs(X.hat) > .25)
```
